The Countercyclical Component of Capital Regulation

### 2020-05-10 Analysis/Draft/Draft_bookdown.Rmd

To shed light on the importance of *Capital savings*, I regress all the components of capital ratio on GDP growth rate. The capital ratio decomposition is shown in equation \ref{eq:decomposition}. The contribution of each component to the cyclicality of the capital ratio is the ratio of their estimated coefficient to the coefficient for the capital ratio regression. To guarantee that the sum of all effects add up to 100\%, I use in this analysis the non-winsorized data and restrict the sample to banks which I observe their capital ratio. Although the coefficient for *Capital savings* are no longer statistically significant, Table \ref{tab:contribution} shows that *Capital savings* are the only countercyclical component of capital ratios. The economic magnitude is also meaningful: *Capital savings* reduce the procyclicality of capital ratios by 11.6\%.

@@

stargazer(reg.list,
          title = "Capital Savings Effect on Capital Ratio Procyclicality",
          table.layout = "n=c=d#-t-as-",
          notes = "\\parbox[t]{16cm}{The table shows estimates for the following model: \\newline \\begin{equation*}\\Delta \\text{Log RWA}_{i,j,t}^{s} = \\beta \\Delta\\text{Log GDP}_{i,t}+\\alpha_{i}+\\alpha_{t}+\\varepsilon_{i,t}. \\end{equation*} \\newline  Each column uses one component of the capital ratio according to equation \\ref{eq:decomposition} as dependent variable. $\\Delta\\text{Log GDP}_{i,t}$ is the real GDP per capita growth rate.  All regressions include bank and year fixed effects. Robust standard errors adjusted for clustering at the country level are reported in parentheses. *, **, and *** indicate statistical significance at the 10\\%, 5\\%, and 1\\% level respectively.}",

          dep.var.labels   = dep.text2,
          covariate.labels = ind.text,
          #se               = se.list,
          add.lines        = fe.list.car,
          #keep            = c("log.gdp_gr"),
          keep.stat        = c("n","rsq"),
          header           = FALSE, 
          type             = "latex",
          font.size        = "footnotesize",
          notes.label      = "",
          notes.align      = "c", 
          notes.append     = FALSE,
          label            = "tab:contribution",
          style            = "qje",
          column.sep.width = "2pt",
          #float.env        = "sidewaystable",
          align            = TRUE)

>>>>

To shed light on the importance of *Capital savings*, I regress all the components of capital ratio on GDP growth rate. The capital ratio decomposition is shown in equation \ref{eq:decomposition}. The contribution of each component to the cyclicality of the capital ratio is the ratio of their estimated coefficient to the coefficient for the capital ratio regression. To guarantee that the sum of all effects add up to 100\%, I use in this analysis the non-winsorized data and restrict the sample to banks which I observe their capital ratio. Although the coefficient for *Capital savings* are no longer statistically significant, Table \ref{tab:contribution} shows that *Capital savings* are the only countercyclical component of capital ratios. The economic magnitude is also meaningful: *Capital savings* reduce the procyclicality of capital ratios by 23.7\%.

@@

stargazer(reg.list,
          title = "Capital Savings Effect on Capital Ratio Procyclicality",
          table.layout = "n=c=d#-t-as-",
          notes = "\\parbox[t]{16cm}{The table shows estimates for the following model: \\newline \\begin{equation*}\\Delta \\text{Log RWA}_{i,j,t}^{s} = \\beta \\Delta\\text{Log GDP}_{i,t}+\\alpha_{i}+\\alpha_{t}+\\varepsilon_{i,t}. \\end{equation*} \\newline  Each column uses one component of the capital ratio according to equation \\ref{eq:decomposition} as dependent variable. $\\Delta\\text{Log GDP}_{i,t}$ is the real GDP per capita growth rate.  All regressions include bank and year fixed effects. Robust standard errors adjusted for clustering at the country level are reported in parentheses. *, **, and *** indicate statistical significance at the 10\\%, 5\\%, and 1\\% level respectively.}",
          dep.var.labels   = dep.text2,
          covariate.labels = ind.text,
          #se               = se.list,
          add.lines        = fe.list.car,
          #keep            = c("log.gdp_gr"),
          keep.stat        = c("n","rsq"),
          header           = FALSE, 
          type             = "latex",
          font.size        = "footnotesize",
          notes.label      = "",
          notes.align      = "c", 
          notes.append     = FALSE,
          label            = "tab:contribution",
          style            = "qje",
          column.sep.width = "2pt",
          #float.env        = "sidewaystable",
          align            = TRUE)
